\section{Research Questions}
\label{sect:rqs}
The work in this paper is gudeied by the following research questions.

\subsubsection*{RQ1: How well do planners' recommendations match developer actions?}
\compactlist
    \item[]\textit{\underline{Motivation}:}~There is no point offering plans that no one will follow.
    Accordingly, on this research question, we ask how many of a planner's recommendations match with the actions taken by developers to fix defects in their files.

    \item[]\textit{\underline{Approach}:}~We measure the \textit{overlap} between the planners' recommendations developers' actions. Then, plot the aggregate number files for overlap values ranging from 0\% to 100\% in bins of size 25\% (for ranges of $0-25\%$, $26-50\%$, $51-75\%$, and $76-100\%$). Planners that have the larger aggregate number files for higher overlap ranges are considered better.

    \item[]\textit{\underline{Evaluation}:}~We compare XTREE with three other outlier statistics based planners from current literature namely, those of \cite{alves}, \cite{shatnawi}, and \cite{oliveira}.
    \medskip
    \item[]\result{XTREE significantly outperforms all other outlier statistics based planners. Further, in all the projects studied here, most of the developers actions to fix defects in a file has a $76-100\%$ overlap with the recommendations offered by XTREE.}
    \compactend
    
\subsubsection*{RQ2: Do planners' recommendations lead to reduction in defects?}
\compactlist
    \item[]\textit{\underline{Motivation}:}~The previous research question measured the extent to which a planner's recommendations matched the actions taken by developers to fix defects in their files. But, a high overlap in most files does not necessarily mean that the defects are actually reduced. Likewise, it is also possible that defects are added due to other actions the developer took during the development. Thus, here we ask how many defects are reduced, and how many are added, in response to larger overlap with the planners' recommendations.

    \item[]\textit{\underline{Approach}:}~Like before, we measure the \textit{overlap} between the planners' recommendations developers' actions. Then, we plot the aggregate number defects reduced in file with overlap values ranging from 0\% to 100\% in bins of size 25\% (for ranges of $0-25\%$, $26-50\%$, $51-75\%$, and $76-100\%$). Planners that have a large number defects reduced for higher overlap ranges are considered better.
 
    \item[]\textit{\underline{Evaluation}:}~Similar to RQ1, we compare XTREE with three other outlier statistics based planners of Alves et al., Shatnawi, and Oliveira, for the overall number of defects reduced and number of defects added.
    \medskip
    \item[]\result{Plans generated by XTREE are superior to other outlier statistics based planners in all 10 projects. Planning with XTREE leads to the far larger number of defects reduced as opposed to defects added in 9 out of 10 projects studied here.}
\compactend

\subsubsection*{RQ3: Are cross-project plans generated by BELLTREE as effective as within-project plans of XTREE?}
\compactlist
    \item[]\textit{\underline{Motivation}:}~The previous research questions we assume that there exists historical data to construct the planning algorithms. However, given the pace of software change, for new projects, it is quite possible that there is insufficient historical data to perform planning. Thus, this research question asks if it is possible to use data from other software projects to construct planners to generate recommendations.
    \item[]\textit{\underline{Approach}:}~We use a cross-project planner that discovers the \textit{bellwether} dataset. Using this bellwether project, we construct XTREE as generate plans as usual. We refer to this combination of using Bellwethers with XTREE as BELLTREE.
    \item[]\textit{\underline{Evaluation}:}~Here we compare BELLTREE with a conventional XTREE and with one other outlier statistics based planner (Shatnawi) to measure the number of defects reduced and number of defects added.
    \medskip
    \item[]\result{The effectiveness of BELLTREE is comparable to the effectiveness of XTREE. In 8 out of 17 BELLTREE outperformed XTREE and 9 out of 17 cases, XTREE outperformed BELLTREE. BELLTREE and XTREE outperformed other planners in all cases.}
\compactend

